Hunting experience and prey predictability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-05-19 manuscript/Chapter3-manuscript.Rmd
update MS and bib. Knit MS. dump file

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002, @schreiberCommunityEffectsPhenotypic2011, @pettorelliChapterTwoIndividual2015, @Michalko.Pekar2016]. Indeed, predator populations are often composed of an assemblage of individuals that specialize in different foraging strategies or resources [@estesIndividualVariationPrey2003, tinkerFoodLimitationLeads2008, kernaleguenDeterminantsIndividualForaging2015, @phillipsCausesConsequencesIndividual2017]. It is now well established that individual foraging specialization cannot be attributed exclusively to instrinsic factors such as sexual, morphological, or age-related differences [@estesIndividualVariationPrey2003, bolnickEcologyIndividualsIncidence2003, Woo.etal2008, bolnickWhyIntraspecificTrait2011]. A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, may instead act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011, @toscanoPersonalityForagingBehavior2016]. Yet, we have very limited knowledge on how intrinsic factors and interactions with prey reciprocally affect predator foraging specialization, and the underlying ecological and fitness consequences of such among-individual differences [@phillipsCausesConsequencesIndividual2017].

sexual, morphological, or age-related differences, while environmental heterogeneity is a prevailing external factor [@Weimerskirch2007, @ceiaIndividualSpecializationForaging2015, @phillipsCausesConsequencesIndividual2017, @Patrick.etal2021].

A potential consequence of among-individual differences in foraging behavior is that they can lead to individual differences in the type of prey captured (i.e. individual niche specialization) [Woo et al., 2008, sources]. There may thus exist a functional relationship linking individual foraging specialisation to specialisation in resource consumption [sources: Toscano et al. 2016, etc, michalko et gibbons, Kerr, Tinker, Bowen]. This would imply that predators need to develop foraging tactics that are fine tuned to specific prey attributes or prey types [sources: Phillips, Woo, etc.]. *ICI GARDER LES IDÉES MAIS METTRE L'ACCENT SUR LE FAIT QUE C'EST LES PROIES DISPONIBLES AU LIEU DES PROIES MANGÉES*

For instance, predators species often use stereotyped hunting techniques required to capture the type of prey they encounter, such as (dauphins, orcas, etc) [sources : Woo, Estes, tinker, etc]. However, it remains largely unclear how extrinsinc and intrinsinct factors interact to shape these individual differences. Therefore, we still have limited knowledge on how individual foraging specialisation arises, and its ecological and community consequences.

@@

@@

# Dernier paragraphe intro (Thèsez-vous)
Here, we collected individual behavioural data from players in *Dead by Daylight* to investigate how hunting experience and the behavioural variation in prey encountered shaped predator foraging specialization. This enabled us to have a high degree of precision on the interaction as both the behaviour of the predator and the four prey were measured simultaneously in each trial. First, we hypothesize that individual predator behaviour will change with hunting experience. If experience reduces the costs of switching between hunting tactics, then predators should become more flexible through time. Alternatively, if experience enables the refinement of the hunting tactics, then individuals may instead specialize through time. Second, we hypothesize that prey behaviour will shape the developmental trajectories of the predator hunting tactics. Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize on prey that are more variable. Third, if individuals differ in their degree of foraging specialization, then we expect that the success of foraging specialists and generalists will be equal. Specialist hunters should fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.

>>>>

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002;@schreiberCommunityEffectsPhenotypic2011;@pettorelliChapterTwoIndividual2015;@Michalko.Pekar2016]. Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources [@estesIndividualVariationPrey2003;@tinkerFoodLimitationLeads2008;@kernaleguenDeterminantsIndividualForaging2015:@Phillips.etal2017]. It is now well established that individual foraging specialization cannot be attributed exclusively to intrinsic factors such as sexual, morphological, or age-related differences [@estesIndividualVariationPrey2003;@bolnickEcologyIndividualsIncidence2003; @Woo.etal2008;@bolnickWhyIntraspecificTrait2011]. A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, may instead act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011;@toscanoPersonalityForagingBehavior2016]. For instance, predators species often use hunting techniques that are fine-tuned to the type of prey that they encounter [sources : Woo, Estes, tinker, etc] (*and the capacity to learn these strategies may be an important limiting factor to be successful*). Yet, we have very limited knowledge on how intrinsic factors and interactions with prey reciprocally affect predator foraging specialization, and the resulting ecological and fitness consequences of such among individual differences [@Phillips.etal2017].

environmental heterogeneity is a prevailing external factor [@Weimerskirch2007;@ceiaIndividualSpecializationForaging2015;@Phillips.etal2017;@Patrick.etal2021].

This would imply that predators need to develop foraging tactics that are fine tuned to specific prey attributes or prey types [sources: Phillips, Woo, etc.]. *ICI GARDER LES IDÉES MAIS METTRE L'ACCENT SUR LE FAIT QUE C'EST LES PROIES DISPONIBLES AU LIEU DES PROIES MANGÉES*

For instance, predators species often use stereotyped hunting techniques required to capture the type of prey they encounter, such as (dauphins, orcas, etc) [sources : Woo, Estes, tinker, etc]. However, it remains largely unclear *accent sur le fait que on est pas sur les mécanismes qui associe la proie à la tactique*

@@

Here, we collected individual behavioural data from players in *Dead by Daylight* to investigate how hunting experience and the behavioural variation in prey encountered shaped predator foraging specialization. This enabled us to have a high degree of precision on the interaction as both the behaviour of the predator and the four prey were measured simultaneously in each trial. First, we hypothesize that individual predator behaviour will change with hunting experience. If experience reduces the costs of switching between hunting tactics, then predators should become more flexible through time. Alternatively, if experience enables the refinement of the hunting tactics, then individuals may instead specialize through time. Second, we hypothesize that prey behaviour will shape the developmental trajectories of the predator hunting tactics. Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize on prey that are more variable. Third, if individuals differ in their degree of foraging specialization, then we expect that the success of foraging specialists and generalists will be equal. Specialist hunters should fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.

# Squelette de l'intro

@@
